Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-10-13 paper/sections/proof-reconstruction.tex
[ paper ] negate rule added.

@@

% % ------------------------------------------------------------------------

@@

% \subsubsection{Normal Forms.}
% \label{sssec:normal_forms}
% \change{Here lacks of an introduction!}
% A negative normal form for the formula φ is one in which negations
% appear only in the literals and the expression is in terms only of
% the boolean operators (¬, ∧, ∨).

>>>>

% -------------------------------------------------------------------

\subsubsection{Negate.}

Each proof of a subgoal is a refutation, thereby each proof assumes
the negation of its subgoal. The \negate rule
assumes the negation of such subgoals. This rules always
appears after apply the \strip inference to the goal.

\begin{verbatim}
fof(goal, conjecture, (p & q)).
fof(subgoal_0, plain, (p), inference(strip, [], [goal])).
fof(subgoal_1, plain, (p => q), inference(strip, [], [goal])).
fof(negate_0_0, plain, (~ p), inference(negate, [], [subgoal_0])).
\end{verbatim}

Then, to emulate this rule, we just introduce the negation
of the subgoal by using the assume rule from the inferences in
Fig.~\ref{fig:CPL-inference-rules}.

@@

% ------------------------------------------------------------------------

@@

\subsubsection{Normalization.}
\label{sssec:normal_forms}
\change{Here lacks of an introduction!}
A negative normal form for the formula φ is one in which negations
appear only in the literals and the expression is in terms only of
the boolean operators (¬, ∧, ∨).
